Parallel Adaptive Importance Sampling

### 2016-06-02 PAIS.tex
Conclusions

***REWRITE***

We have explored the application of parallelised MCMC algorithms in
low dimensional inverse problems. We have demonstrated numerically
that these algorithms converge faster than the analogous naively parallelised
Metropolis-Hastings algorithms. Further experimentation with the
Random Walk Metropolis-Hastings (RWMH), Metropolis Adjusted Langevin
Algorithm (MALA) and preconditioned Crank-Nicolson (pCN) proposals has
yielded similar results\cite{Paul}.

@@

One limitation of the PAIS approach as described above is that a
direct solver (such as FastEMD \cite{FastEMD}) has computational cost
$\mathcal{O}(n^3\log n)$, where $n$ is the number of particles in the
ensemble.  The use of approximate solutions from iterative solvers
might allow the PAIS to be used in higher dimensional problems, and is
an avenue for future investigation. A second limitation is associated
with the problem of accurately approximating measures with empirical
measures in high dimensional phase space. This is a well-known issue
in filtering, where one possible solution is to ``localise'' the
impact of observations, as rigorously analysed in
\cite{rebeschini2013can}. An established technique in Ensemble Kalman
filters, localisation has also been incorporated into the Ensemble
Transform Particle Filter \cite{ChRe2015}. This issue could be
addressed in the PAIS by using localisation when computing the
transform, but keeping the unlocalised weights in the importance
sampling for consistency.

>>>>

We have explored the application of parallelised MCMC algorithms in
low dimensional inverse problems. We have demonstrated numerically
that these algorithms converge faster than the analogous naively parallelised
Metropolis-Hastings algorithms. Further experimentation with the
Random Walk Metropolis-Hastings (RWMH), Metropolis Adjusted Langevin
Algorithm (MALA), preconditioned Crank-Nicolson (pCN) and Hamiltonian
Monte Carlo (HMC) proposals has
yielded similar results\cite{Paul}.

@@

One limitation of the PAIS approach as described above is that a
direct solver of the ETPF problem (such as FastEMD \cite{FastEMD}) has computational cost
$\mathcal{O}(M^3\log M)$, where $M$ is the number of particles in the
ensemble. As such, we introduced a more approximate resampler the
approximate multinomial resampler, which allows us to push the
approach to the limit
with much larger ensemble sizes. The PAIS framework is very flexible
in terms of being able to use any combination of proposal
distributions and resampling algorithms that one wishes.

%  A second limitation is associated
% with the problem of accurately approximating measures with empirical
% measures in high dimensional phase space. This is a well-known issue
% in filtering, where one possible solution is to ``localise'' the
% impact of observations, as rigorously analysed in
% \cite{rebeschini2013can}. An established technique in Ensemble Kalman
% filters, localisation has also been incorporated into the Ensemble
% Transform Particle Filter \cite{ChRe2015}. This issue could be
% addressed in the PAIS by using localisation when computing the
% transform, but keeping the unlocalised weights in the importance
% sampling for consistency.
